A Review on Multi-Label Learning Algorithms

### 2018-01-15 Paper/Presentation/mll_review.tex
Minor updates

\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Problem Definition}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Introduction}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Single-label supervised learning
\begin{itemize}
\item Applied to classification
\item Supervised: Dataset $\{ (x_i, y_i)\}, i = 1, \dots N, x \in X, y \in Y$
\item Goal is to learn a model $f: X \rightarrow Y$
\end{itemize}

Multi-label supervised learning
\begin{itemize}
\item Multiple labels per instance: $\{ (x_i, \bm{y}_i)\}, i = 1, \dots N, x \in X, \bm{y} \in \mathbb{P}(Y)$
\item Learn a model $f: X \times Y \rightarrow r$ where $r\in \mathbb{R}$ is the confidence that $y_i$ characterizes $x_i$
\item For classification, assume that $x_i$ belongs to $y_i$ if $r \ge $ $t(x_i)$

\begin{itemize}
\item $t(\cdot)$ can be a predetermined constant function or learned from $X$
\end{itemize}

\end{itemize}
TODO: Include stuff about multi-labeled dataset characterization?
\end{frame}
%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
\item e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

\begin{enumerate}
\item First-order strategies
\begin{itemize}
\item Transform multi-labeled problem to multiple, single-label problems
\item Ignore label correlations
\item Simple, scalable, suboptimal
\end{itemize}
\item Second-order strategies
\begin{itemize}
\item Consider \emph{pairwise} label relations
\item Good trade-off between generalization performance and scalability
\item Lacking in some real-world applications
\end{itemize}
\item Higher-order strategies
\begin{itemize}
\item Capture more complicated label interdependencies
\item Strong modeling capabilities
\item Computationally demanding, less scalable
\end{itemize}

@@

%------------------------------------------------
\subsection{Evaluation Metrics}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Two categories and perspectives:
\begin{itemize}
\item \emph{Example-based: }Evaluates multi-labelled performance on each example, extrapolate to whole dataset
\begin{itemize}
\item \emph{Classification perspective:}
\begin{itemize}
\item Subset Accuracy, Hamming Loss
\item Precision, Recall, F-measure, F$^\beta$ -measure
\end{itemize}
\item \emph{Ranking perspective:} one-error, coverage, ranking loss, average precision
\end{itemize}
\item \emph{Label-based: }Evaluates performance on each label separately, extrapolate to whole label set
\begin{itemize}
\item Classification perspective: Macro/Micro averaging for single-label example-based, classification-based measures
\item Ranking perspective: Macro/Micro averaging for AUC
\end{itemize}
\end{itemize}
Classifiers should aim to optimize \emph{multiple} metrics
\end{frame}
%------------------------------------------------
\section{Multi-label Learning Algorithms}
%------------------------------------------------
\subsection{Categorization}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Multi-label Learning Algorithms}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}

@@

Include algorithms that:
\begin{itemize}
\item Has broad, unique characteristics
\item Has primitive impact, i.e. leads to a number follow-up related methods
\item Is influential and highly-cited in multi-label learning
\end{itemize}

@@

\item Predict labels of an unseen $x$ by evaluating each classifier $h_i(x)$
\item Output labels where  $h_i(x) > 0$ or $\underset{1 \geq i \geq q}{argmax} \{h_i(x))\}$, if none
\end{itemize}

@@

\begin{frame}
\frametitle{Classifier chains}
\begin{itemize}
\item A permutation function $f_p$ is used to order $Y$
\item Transform into a \emph{chain} of binary classification problems
\item Enrich representations at each step $j$ by concatenating each $x_i$ with the confidence of the $j$-th classifier
\item Predict relevant labels for unknown instances by iteratively traversing the classifier chain
\end{itemize}

Pros \& cons:
\begin{itemize}
\item Higher-order method: exploitation of label correlations, but in a random manner
\item Highly sensitive to $f_p$. Ensemble schemes attempt to overcome it.
\item Iterative operation prevents parallel implementation
\end{itemize}
\end{frame}
%------------------------------------------------

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item Transform into a label pairwise comparison ranking problem
\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
\item Construct training sets $D_{jk} : \{x_i | y_j \in Y_i \oplus y_k \in Y_i\}$
\item For an unknown instance, all classifiers' votes are aggregated and ranked
\item A virtual label $y_v$ serves as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
\item Second-order approach algorithm. One-vs-one scheme.
\item Smooths out the class-imbalance problem
\item Number of classifiers s quadratic to $|Y|$ (compared to linear for BR)
\begin{itemize}
\item Pruning methods to reduce the search space
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item Decompose to an ensemble of multi-class classification problems
\item Each component targets a random subset of $Y$, classified with Label Powerset (LP) techniques:
\begin{itemize}
\item Transform to single-label data by treating each distinct labelset as a new class
\item Each example is reassigned with the mapped single-label participating in multi-class classifier induction
\item For unknown $x$, counts the maximum and actual number of votes
\item Label set is relevant when the number of votes exceeds half of the max
\end{itemize}
\end{itemize}
Pros \& cons:
\begin{itemize}
\item High-order approach algorithm
\item Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
\item Large $Y$ implies high training complexity.
\item Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.75]{images/aa.png}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
\item First-order approach algorithm, adapting knn techniques
\item Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$
\item Priors $P(K)$ computed by smoothed frequency estimation in the training data
\item Likelihoods $P(C_j|K)$ are computed as a function of:
\begin{itemize}
\item $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
\item $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
\end{itemize}
\end{itemize}

@@

>>>>

\section{Introduction} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
\subsection{Multi-label learning}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Introduction}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Applied to supervised classification
\begin{itemize}
\item Given input data and labels, goal is to learn a model $f: X \rightarrow Y$ 
\item $f(x_i, y_i) = r$ where $r\in \mathbb{R}$ is the confidence that $y_i$ characterizes $x_i$
\item Assume that $x_i$ belongs to $y_i$ if $r \ge $ $t(x_i)$
\begin{itemize}
  \item $t(\cdot)$ can be a predetermined constant function or learned from $X$
\end{itemize}
\end{itemize}

Single-label learning
\begin{itemize}
	\item Dataset $\{ (x_i, y_i)\}, i = 1, \dots N, x \in X, y \in Y=\{y_1,\dots,y_q\}$
\end{itemize}

Multi-label learning
\begin{itemize}
\item Multi-label dataset: Multiple labels per instance. $\{ (x_i, \bm{y}_i)\}, i = 1, \dots N, x \in X, \bm{y} \in \mathbb{P}(Y)$
% \item Learn a model $f: X \times Y \rightarrow r$

\end{itemize}
%TODO: Include stuff about multi-labeled dataset characterization?
\end{frame}
%------------------------------------------------
%------------------------------------------------
\subsection{Algorithm Strategies}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Label search space $\mathbb{S_Y}$ grows exponentially as a function of $|Y|=q$
\begin{itemize}
\item e.g. for $q=20, |\mathbb{S_Y}| = 2 ^ {|\mathbb{P(Y)}|} = 2^{20} \ge 10^6$
\end{itemize}
Solution: integrate in the learning process potential label correlations.
This work examines algorithms grouped in three broad categories:

\begin{enumerate}
\item First-order strategies
\begin{itemize}
\item Ignore label correlations
\item Often transform M-L problem to multiple, single-label problems
\item Simple, scalable, suboptimal
\end{itemize}
\item Second-order strategies
\begin{itemize}
\item Consider \emph{pairwise} label relations
\item Good trade-off between generalization performance and scalability
\item Lacking in some real-world applications
\end{itemize}
\item Higher-order strategies
\begin{itemize}
\item Capture more complicated label interdependencies
\item Strong modeling capabilities
\item Computationally demanding, less scalable
\end{itemize}

@@

%------------------------------------------------
\subsection{Evaluation Metrics}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
Extension of single-label metrics to the M-L case.

Two categories and perspectives:
\begin{itemize}
\item \emph{Example-based: }Evaluates multi-labelled performance on each example, extrapolate to whole dataset
\begin{itemize}
\item \emph{Classification perspective:}
\begin{itemize}
\item Subset Accuracy, Hamming Loss
\item Precision, Recall, F-measure, F$^\beta$ -measure
\end{itemize}
\item \emph{Ranking perspective:} one-error, coverage, ranking loss, average precision
\end{itemize}
\item \emph{Label-based: }Evaluates performance on each label separately, extrapolate to whole label set
\begin{itemize}
\item Classification perspective: Macro/Micro averaging for single-label example-based, classification-based measures
\item Ranking perspective: Macro/Micro averaging for AUC
\end{itemize}
\item[\rightarrow] Classifiers should aim to optimize \emph{multiple} metrics
\end{itemize}
\end{frame}
%------------------------------------------------
\section{Multi-label Learning Algorithms}
%------------------------------------------------
\subsection{Categorization}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Multi-label Learning Algorithms}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}

@@

Include algorithms that:
\begin{itemize}
\item Has broad, noteworthy or unique characteristics
\item Has primitive impact, i.e. leads to a number follow-up related methods
\item Is influential and highly-cited in multi-label learning
\end{itemize}

@@

\item Predict labels of an unseen $x$ by evaluating each classifier $h_i(x)$
\item Assign label $y_i$ according to $h_i(x)$ and the thresholding/ranking scheme 
\end{itemize}

@@

\begin{frame}
\frametitle{Classifier chains}
\begin{itemize}
\item A permutation function $f_p$ is used to order $Y$
\item Transform into a \emph{chain} of binary classification problems
\item Enrich representations at step $j$ by concatenating each $x_i$ with the confidence of preceeding $1,\dots,j-1$-th classifiers
\item Predict relevant labels for unknown instances by iteratively traversing the classifier chain
\end{itemize}
todo prediction

Pros \& cons:
\begin{itemize}
\item Higher-order method: exploitation of label correlations to a degree, but in a random manner
\item Highly sensitive to $f_p$. Ensemble schemes attempt to overcome it.
\item Iterative operation prevents parallel implementation
\end{itemize}
\end{frame}
%------------------------------------------------

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
\item Transform into a label pairwise comparison ranking problem
\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
\item Construct training sets $D_{jk} : \{x_i, Y_i | y_j \in Y_i \oplus y_k \in Y_i\}$
\item For an unknown instance, all classifiers' votes are aggregated and ranked
\item A virtual label $y_v$ serves as the artificial splitting point between relevant and irrelevant labels
\end{itemize}
todo how it works exactly cardum
Pros \& cons:
\begin{itemize}
\item Second-order approach algorithm. One-vs-one scheme.
\item Smooths out the class-imbalance problem
\item Number of classifiers s quadratic to $|Y|$ (compared to linear for BR)
\begin{itemize}
\item Pruning methods to reduce the search space
\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
\item Decompose to an ensemble of multi-class classification problems
\item Each component targets a random subset of $\mathbb{P}(Y)$ that appears in $X$, classified with Label Powerset (LP) techniques:
\begin{itemize}
\item Transform to single-label data by treating each distinct labelset as a new class
\item Each example is reassigned with the new mapped class and classified through regular single-label classification
\item M-L classify $x$ with $y_i$ when the votes received for $y_i$ from the ensemble exceed half the max possible it can get
\end{itemize}
todo how does each LP classify, k-labelsets
\end{itemize}
Pros \& cons:
\begin{itemize}
\item High-order approach algorithm
\item Data-sensitive: Cannot generalize to labelsets not in the training set, too few examples for some labelsets
\item Large $Y$ implies high training complexity.
\item Improve by invoking an ensemble on random k-sized labelsets
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{figure}
\begin{center}
\includegraphics[scale = 0.75]{images/aa.png}
\end{center}
\end{figure}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
\item First-order approach algorithm, adapting knn techniques
\item Compares the MAP probabilities: $P(K|C_j), K \in \{H_j, \neg H_j\}$
\item Priors $P(K)$ computed by smoothed frequency estimation in the training data
\item Likelihoods $P(C_j|K)$ are computed as a function of:
\begin{itemize}
\item $\kappa(r)$, the number of examples labelled $y_j$ with $r$ neighbours labelled $y_j$
\item $\overset{\sim}{\kappa}(r)$, the number of examples not labelled $y_j$ with $r$ neighbours labelled $y_j$
\end{itemize}
\end{itemize}

@@

%------------------------------------------------
\subsection{Related Work}
\begin{frame}
\frametitle{\insertsection : \insertsubsection}
\begin{itemize}
\item Madjarov, Gjorgji, et al. "An extensive experimental comparison of methods for multi-label learning." Pattern Recognition 45.9 (2012): 3084-3104
\item Tsoumakas, Grigorios, and Ioannis Katakis. "Multi-label classification: An overview." International Journal of Data Warehousing and Mining 3.3 (2006)
\item Zhang, Min-Ling, and Kun Zhang. "Multi-label learning by exploiting label dependency." Proceedings of the 16th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2010
\end{itemize}
\end{frame}
